---
title: "Vignette-NeuralNetwork"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette-NeuralNetwork}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(NeuralNetwork)
```
## Functionality
This package provides functionality to

* built user-defined feedforward Neural Networks for classification and regression
* use different activation functions
* choose between different algorithms
* split data into test- and trainsets
* visualize the Neural Network
<br>


# Usage

## 1. Create a Neural Network 

```
R6 Class Representing a Neural Network

NeuralNet <- R6::R6Class("NeuralNet",
public = list(inputsize = NULL, weights = list(), bias = list(), nrhiddenlayers = NULL, actfct = NULL, dActfct = NULL, outputfct = NULL, category = NULL)) 

  @param inputsize size of the input for the Neural Network (1st layer of nodes)
  
  @param weights ist of matrices representing the weights of the connections
         between nodes.

  @param bias list of vectors representing the biases for nodes.
  
  @param nrhiddenlayers number of hidden layers of the Neural Network.
  
  @param actfct string matching predefined activation function or
         other function, see \code{Activation Functions}.
         
  @param dactfct NULL, when using predefined Activation functions, or
         the derivative of a custom Activation function, it is not checked for
         correcteness. (dactfct = Deactivation Function)
         
  @param outputfct string matching predefined activation function or
         other a function, see \code{Activation Functions}, used as activation
         function for the last layer of nodes
         
  @param category string matching valid category for Neural Network, either
         classification or regression.

```

<br>

### examples

This will generate a Neural Network with two input nodes, two output nodes and two hidden layers with four nodes each:

`nn.1 <- NeuralNet$new(c(2,4,4,2))`

<br>

This will generate a Neural Network using the predefined sigmoid function as
activation function for all layers, including the output-layer:


`nn.2 <- NeuralNet$new(c(2,4,4,2), activationfct = "sigmoid", outputfct = "sigmoid")`

## 2. Configure Optimizer

You can choose between three optimizer algorithms:

* Stochastic Gradient Descent 
```
OptimizerSGD <- R6::R6Class("OptimizerSGD",
private = list(learning_rate = 0, regularization_rate = 0)


```

* Stochastic Gradient Descent with Momentum

```
OptimizerMomentum <- R6::R6Class("OptimizerMomentum",
private = list(
  learning_rate = 0,
  regularization_rate = 0,
  momentum_term = 0,
  weightMomentum = NULL,
  biasMomentum = NULL
)
```

* Nesterov accelerated gradient


```

OptimizerNesterovAG <- R6::R6Class("OptimizerNesterovAG",private = list(
   learning_rate = 0,
   regularization_rate = 0,
   momentum_term = 0,
   weightMomentum = NULL,
   biasMomentum = NULL
 )
 
```

### examples

This will generate a Stochastic Gradient Descent with Momentum Optimizer with a learning_rate of 0.0005, regularization_rate of 0 and a momentum_term of 0:
 
`optimizer <- OptimizerMomentum$new(0.0005, 0, 0.9)`

<br>

The previous set values can be changed:
```
   optimizer$setLearningRate(0.0001)
   optimizer$setRegularizationRate(0.00001)
   optimizer$setMomentumTerm(0.8)
```

## 3. Prepare Data


